\documentclass[11pt]{article}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{titling}
\usepackage{amsmath,amssymb}
\usepackage{authblk}
\usepackage{longtable}
\usepackage[T1]{fontenc}

\setlength{\droptitle}{-10em}

\title{\bf Chemical abundances and radial velocities for candidate co-moving
stars}

\author{
  Semyeong Oh (Co-PI, \texttt{semyeong@astro.princeton.edu})
  \and
  Adrian M. Price-Whelan (Co-PI, \texttt{adrn@astro.princeton.edu})
}

\date{}

\begin{document}
\maketitle

\section*{Co-Is}

\begin{itemize}
    \item Melissa Ness, Max Planck Institute for Astronomy, Germany
    \item David W. Hogg, New York University, USA
    \item Hans-Walter Rix, Max Planck Institute for Astronomy, Germany
\end{itemize}

\section*{External Collaborators: Requests for External Status}

Adrian M. Price-Whelan: EC requests will be submitted with this proposal.

Adrian M. Price-Whelan has expertise in statistical inference and dynamical
modeling of the Milky Way.

He is an SDSS-III architect for his contributions to the
science archive server, data management software, and observation management
software used by the SDSS observers.

\section{Scientific and technical justification}

\subsection{Summary}

Our main goal is to obtain radial velocities and detailed chemical abundances
for high-confidence, candidate co-moving star pairs selected using parallaxes
and proper motions from the Tycho-Gaia Astrometric Solution (TGAS).
We will use radial velocity measurements of each star in the observed candidate
pairs to identify true co-moving pairs, which span a large range of physical
separations ($\approx$0.01--10 pc).
Widely-separated, co-moving star pairs are likely loosely-bound or
recently-unbound, co-eval but non-interacting stars.
Confirmed co-moving pairs will be used to (a) study the disruption of
widely-separated binary stars and subsequent evolution in the Galactic tidal
field, (b) test predictions for chemical homogeniety and the prospects of
chemical tagging, and (c) validate stellar models, including results from
the APOGEE pipeline (abundances and age indicators).

\subsection{Science goals}

TODO:

\subsection{Feasibility assessment}

All of our proposed targets are bright ...

Need to observe pairs...

\subsection{Proposal type}

The targets in this proposal fall on planned APOGEE-2 pointings, thus, our
request is a {\bf Type 1} proposal.

\section{Type 1 Target Information}

We propose to observe 137 stars with $H>7$~mag within existing fields
from two categories:
\begin{itemize}
  \item 65 pairs (130 stars) for which both of the member stars falls
  within the existing fields
  \item 7 additional stars for which the other star in the pairs is aleady
  observed in APOGEE DR12
\end{itemize}
%
There are 21 pairs in the first category whose angular separation is smaller
than 72~arcseconds, the fiber collision threshold. However, given the
brightnesso f these stars, they should be able to reach signal-to-noise ratio
per resolution element over 100 with a single visit.

Mention false-positive rate constraint from RAVE

\input{targets.tex}

\section{1m Target Information}

TODO:

\section{References}

TODO:

\end{document}
